### 2020-05-17 writeup/transfer.tex
wip

\section{Illustrative Examples and Their Insights on Transfer}\label{sec_insight}

@@

\begin{proposition}\label{prop_data_size}
	In the setting of Example \ref{ex_basic}, assume that $c_1 \ge 100$ and $c_2  \ge 3$ are fixed constants.
	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
	\begin{itemize}
		\item If $c_2 < \frac{2\sigma^2}{3p d^2} + 1$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
		\item If $c_2 > \frac{3\sigma^2}{2p d^2} + 1$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $100 \le c_1 < \frac{(c_2-2)\sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{c_2 \sigma^2}{2(c_2 - 1)p d^2/3 - \sigma^2}$ and $c_1\ge 110$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$. {\cor (cannot get this because we only have some bounds. If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
\end{proposition}

\textbf{Implications.}

>>>>

\section{Dissecting the Effects of Different Task Data in Multi-Task learning}\label{sec_insight}

@@

\begin{proposition}\label{prop_data_size}
	In the setting of Example \ref{ex_basic}, assume that $c_1 \ge 100$ and $c_2  \ge 3$ are fixed constants.
	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
	\begin{itemize}
		\item If $d^2 < \frac{2\sigma^2}{3p (c_2 - 1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
		\item If $d^2 > \frac{3\sigma^2}{2p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $100 \le c_1 < \frac{(c_2-2)\sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{c_2 \sigma^2}{2(c_2 - 1)p d^2/3 - \sigma^2}$ and $c_1\ge 110$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$. {\cor (cannot get this because we only have some bounds. If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
\end{proposition}

The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
An intuitive interpretation of Proposition \ref{prop_data_size} is that:
i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.

\textbf{Implications.} We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized by a metric called the data efficiency ratio as follows.
Given several tasks, let $\alpha$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha$ factor (compared to training independently) while keeping the performance nearly the same.
We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.

\begin{proposition}\label{prop_data_efficiency}
\end{proposition}
